\thetitle

### 2022-07-13 thesis/paper.tex
typos

\begin{theorem}[\ifen Accuracy of the na\"ive algorithm\else 나이브 해법의 정확성\fi] \label{oneoverhopt}
\ifen 
When the application limit is $h$, let $\mathcal{X}_h$ denote the optimal portfolio, and $\mathcal{T}_h$ the set of the $h$ schools having the largest values of $f_j t_j$. Then $v(\mathcal{T}_h) / v(\mathcal{X}_h) \geq 1/h$. 
\else
지원 제한이 $h$일 때, 최적 포트폴리오가 $\mathcal{X}_h$이고 기대 효용 $f_j t_j$가 가장 큰 $h$개의 학교의 집합이 $\mathcal{T}_h$라고 하자. 그러면 $v(\mathcal{T}_h) / v(\mathcal{X}_h) \geq 1/h$이다.
\fi
\end{theorem}
\begin{proof}
\ifen
Because $\mathcal{T}_h$ maximizes the quantity $\operatorname{E}\bigl[ \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\bigr]$, we have
\else
$\mathcal{T}_h$는 $\operatorname{E}\bigl[ \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\bigr]$를 최대화하므로,
\fi
\begin{align} \label{oneoverhopt}
\begin{split}
v(\mathcal{X}_h) &= \operatorname{E}\Bigl[ \max_{j \in \mathcal{X}_h}\{ t_j Z_j \}\Bigr] \leq \operatorname{E}\Bigl[ \sum_{j \in \mathcal{X}_h}\{ t_j Z_j \}\Bigr] \leq \operatorname{E}\Bigl[ \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\Bigr] \\
&= h  \operatorname{E}\Bigl[ \tfrac{1}{h} \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\Bigr]
\leq h  \operatorname{E}\Bigl[ \max_{j \in \mathcal{T}_h}\{ t_j Z_j \}\Bigr]
= h v(\mathcal{T}_h).
\end{split}
\end{align}
\ifen 
where the final inequality follows from the concavity of the $\max\{\}$ operator.
\else
단, 마지막 부등호는 $\max\{\}$ 연산의 볼록성에 따라 성립한다.
\fi
\end{proof}
\ifen
\noindent The following example establishes the tightness of the approximation factor. 
\else
\noindent 다음 예는 근사 계수가 타이트(tight)함을 보인다.
\fi

\begin{example} \label{tightexampleforoneoverhopt}
\ifen
Pick any $h$ and let $m = 2h$. For a small constant $\varepsilon \in (0, 1)$, define the market as follows.
\else
임의의 $h$를 택하고 $m = 2h$라고 하자. 작은 상수  $\varepsilon \in (0, 1)$에 대해 시장을 다음처럼 구성한다.
\fi
%\begin{align}
% f &= \Bigl(\,\underbrace{1,  \dots, 1}_{h},\;
%\underbrace{\varepsilon^{1}, \varepsilon^{2}, \dots, \varepsilon^{h-1}, \varepsilon^{h}}_{h}\,\Bigr) \\
%\text{\ifen and\else 그리고\fi}\quad t &= \Bigl(\,\underbrace{1,  \dots, 1}_{h},\;
%\underbrace{\varepsilon^{-1}, \varepsilon^{-2}, \dots, \varepsilon^{-(h-1)}, \varepsilon^{-h}}_{h}\,\Bigr) 
%\end{align}
\begin{center}
\begin{tabular}{r|cccccccc}
$j$   & $1$      & $\cdots$ & $h$   &$h+1$         &  $h+2$ & $\cdots$ &      $m-1$  & $m$            \\ \hline
$f_j$ & $1$     &  $\cdots$ & $1$      & $\varepsilon^{1}$ & $\varepsilon^{2}$ & $\cdots$ & $\varepsilon^{h-1}$ & $\varepsilon^{h}$ \\
$t_j$ & $1$      &  $\cdots$ & $1$      & $\varepsilon^{-1}$ & $\varepsilon^{-2}$ & $\cdots$ & $\varepsilon^{-(h-1)}$ & $\varepsilon^{-h}$
\end{tabular}%
\end{center}
\ifen
Since all $f_j t_j = 1$, the na\"ive algorithm can choose $\mathcal{T}_h = \{1, \dots, h\}$, with $v(\mathcal{T}_h) = 1$. But the optimal solution is $\mathcal{X}_h = \{h+1, \dots, m\}$, with
\else
모든 $f_j t_j = 1$이므로 나이브 해법은 $\mathcal{T}_h = \{1, \dots, h\}$를 출력할 수 있으며 $v(\mathcal{T}_h) = 1$이다. 그러나 최적해는 $\mathcal{X}_h = \{h+1, \dots, m\}$이며 그의 기대 효용은 다음과 같다.
\fi
\begin{equation}
v(\mathcal{X}_h) = \sum_{j= h +1}^m \Bigl( f_j t_j \prod_{j' = j+1}^m (1 - f_{j'}) \Bigr) =  \sum_{j= 1}^h  (1 - \varepsilon)^{j} \approx h\ifen.\fi
\end{equation}
\ifen
Thus, as $\varepsilon$ approaches zero, we have $v(\mathcal{T}_h) / v(\mathcal{X}_h) \to 1/h$. (The optimality of $\mathcal{X}_h$ follows from the fact that it achieves the upper bound of Theorem \ref{oneoverhopt}.)
\else
따라서 $\varepsilon$이 0에 가까워지면서 $v(\mathcal{T}_h) / v(\mathcal{X}_h) \to 1/h$이 된다.  ($\mathcal{X}_h$의 최적성은 정리 \ref{oneoverhopt}이(가) 제시하는 상한을 실천하기 때문에 성립한다.)
\fi
\end{example}

@@

Applying Lemma \ref{eliminationtheorem}, we eliminate $c_k$, transform the remaining $t_j$-values to $\bar t_j$ according to \eqref{howtotransformtj}, and obtain a function $w(\mathcal{Y}) = v(\mathcal{Y} \cup \{k\}) - f_k t_k$ that grades portfolios $\mathcal{Y} \subseteq \mathcal{C} \setminus \{k\}$ according to how well they complement $\{k\}$. Since $w(\mathcal{Y})$ is itself a portfolio valuation funtion and $\bar t_0 = 0$, the inductive hypothesis implies that $\mathcal{Y}_{h-1} \subset \mathcal{Y}_h$, which completes the proof.
\else 이제 $k \in \mathcal{X}_h$인 경우를 고려하자. 그러면 크기 $h-1$인 어떤 포트폴리오 $\mathcal{Y}_{h-1}$에 대해 $\mathcal{X}_h = \mathcal{Y}_{h-1} \cup \{k\}$으로 표현할 수 있다. $\mathcal{Y}_{h-1} \subset \mathcal{Y}_h$임을 보이면 충분하다. 정의에 따라 $\mathcal{Y}_{h-1}$ ($\mathcal{Y}_{h}$)는 크기가 $h-1$ ($h$)인 포트폴리오 중에 함수 $v(\mathcal{Y}\cup\{k\})$를 최대화한다. 다시 말해 $\mathcal{Y}_{h-1}$과 $\mathcal{Y}_h$는 각각 단일 원소 포트폴리오 $\{k\}$와 최적으로 보완적인 학교 집합이다.

>>>>

\begin{theorem}[\ifen Accuracy of the na\"ive algorithm\else 나이브 해법의 정확성\fi] \label{oneoverhoptthm}
\ifen 
When the application limit is $h$, let $\mathcal{X}_h$ denote the optimal portfolio, and $\mathcal{T}_h$ the set of the $h$ schools having the largest values of $f_j t_j$. Then $v(\mathcal{T}_h) / v(\mathcal{X}_h) \geq 1/h$. 
\else
지원 제한이 $h$일 때, 최적 포트폴리오가 $\mathcal{X}_h$이고 기대 효용 $f_j t_j$가 가장 큰 $h$개의 학교의 집합이 $\mathcal{T}_h$라고 하자. 그러면 $v(\mathcal{T}_h) / v(\mathcal{X}_h) \geq 1/h$이다.
\fi
\end{theorem}
\begin{proof}
\ifen
Because $\mathcal{T}_h$ maximizes the quantity $\operatorname{E}\bigl[ \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\bigr]$, we have
\else
$\mathcal{T}_h$는 $\operatorname{E}\bigl[ \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\bigr]$를 최대화하므로,
\fi
\begin{align} \label{oneoverhopt}
\begin{split}
v(\mathcal{X}_h) &= \operatorname{E}\Bigl[ \max_{j \in \mathcal{X}_h}\{ t_j Z_j \}\Bigr] \leq \operatorname{E}\Bigl[ \sum_{j \in \mathcal{X}_h}\{ t_j Z_j \}\Bigr] \leq \operatorname{E}\Bigl[ \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\Bigr] \\
&= h  \operatorname{E}\Bigl[ \tfrac{1}{h} \sum_{j \in \mathcal{T}_h}\{ t_j Z_j \}\Bigr]
\leq h  \operatorname{E}\Bigl[ \max_{j \in \mathcal{T}_h}\{ t_j Z_j \}\Bigr]
= h v(\mathcal{T}_h)\ifen\else.\fi
\end{split}
\end{align}
\ifen 
where the final inequality follows from the concavity of the $\max\{\}$ operator.
\else
단, 마지막 부등호는 $\max\{\}$ 연산의 볼록성에 따라 성립한다.
\fi
\end{proof}
\ifen
\noindent The following example establishes the tightness of the approximation factor. 
\else
\noindent 다음 예는 근사 계수가 타이트(tight)함을 보인다.
\fi

\begin{example} \label{tightexampleforoneoverhopt}
\ifen
Pick any $h$ and let $m = 2h$. For a small constant $\varepsilon \in (0, 1)$, define the market as follows.
\else
임의의 $h$를 택하고 $m = 2h$라고 하자. 작은 상수  $\varepsilon \in (0, 1)$에 대해 시장을 다음처럼 구성한다.
\fi
%\begin{align}
% f &= \Bigl(\,\underbrace{1,  \dots, 1}_{h},\;
%\underbrace{\varepsilon^{1}, \varepsilon^{2}, \dots, \varepsilon^{h-1}, \varepsilon^{h}}_{h}\,\Bigr) \\
%\text{\ifen and\else 그리고\fi}\quad t &= \Bigl(\,\underbrace{1,  \dots, 1}_{h},\;
%\underbrace{\varepsilon^{-1}, \varepsilon^{-2}, \dots, \varepsilon^{-(h-1)}, \varepsilon^{-h}}_{h}\,\Bigr) 
%\end{align}
\begin{center}
\begin{tabular}{r|cccccccc}
$j$   & $1$      & $\cdots$ & $h$   &$h+1$         &  $h+2$ & $\cdots$ &      $m-1$  & $m$            \\ \hline
$f_j$ & $1$     &  $\cdots$ & $1$      & $\varepsilon^{1}$ & $\varepsilon^{2}$ & $\cdots$ & $\varepsilon^{h-1}$ & $\varepsilon^{h}$ \\
$t_j$ & $1$      &  $\cdots$ & $1$      & $\varepsilon^{-1}$ & $\varepsilon^{-2}$ & $\cdots$ & $\varepsilon^{-(h-1)}$ & $\varepsilon^{-h}$
\end{tabular}%
\end{center}
\ifen
Since all $f_j t_j = 1$, the na\"ive algorithm can choose $\mathcal{T}_h = \{1, \dots, h\}$, with $v(\mathcal{T}_h) = 1$. But the optimal solution is $\mathcal{X}_h = \{h+1, \dots, m\}$, with
\else
모든 $f_j t_j = 1$이므로 나이브 해법은 $\mathcal{T}_h = \{1, \dots, h\}$를 출력할 수 있으며 $v(\mathcal{T}_h) = 1$이다. 그러나 최적해는 $\mathcal{X}_h = \{h+1, \dots, m\}$이며 그의 기대 효용은 다음과 같다.
\fi
\begin{equation}
v(\mathcal{X}_h) = \sum_{j= h +1}^m \Bigl( f_j t_j \prod_{j' = j+1}^m (1 - f_{j'}) \Bigr) =  \sum_{j= 1}^h  (1 - \varepsilon)^{j} \approx h\ifen.\fi
\end{equation}
\ifen
Thus, as $\varepsilon$ approaches zero, we have $v(\mathcal{T}_h) / v(\mathcal{X}_h) \to 1/h$. (The optimality of $\mathcal{X}_h$ follows from the fact that it achieves the upper bound of Theorem \ref{oneoverhoptthm}.)
\else
따라서 $\varepsilon$이 0에 가까워지면서 $v(\mathcal{T}_h) / v(\mathcal{X}_h) \to 1/h$이 된다.  ($\mathcal{X}_h$의 최적성은 정리 \ref{oneoverhoptthm}이(가) 제시하는 상한을 실천하기 때문에 성립한다.)
\fi
\end{example}

@@

Applying Lemma \ref{eliminationtheorem}, we eliminate $c_k$, transform the remaining $t_j$-values to $\bar t_j$ according to \eqref{howtotransformtj}, and obtain a function $w(\mathcal{Y}) = v(\mathcal{Y} \cup \{k\}) - f_k t_k$ that grades portfolios $\mathcal{Y} \subseteq \mathcal{C} \setminus \{k\}$ according to how well they complement $\{k\}$. Since $w(\mathcal{Y})$ is itself a portfolio valuation function and $\bar t_0 = 0$, the inductive hypothesis implies that $\mathcal{Y}_{h-1} \subset \mathcal{Y}_h$, which completes the proof.
\else 이제 $k \in \mathcal{X}_h$인 경우를 고려하자. 그러면 크기 $h-1$인 어떤 포트폴리오 $\mathcal{Y}_{h-1}$에 대해 $\mathcal{X}_h = \mathcal{Y}_{h-1} \cup \{k\}$으로 표현할 수 있다. $\mathcal{Y}_{h-1} \subset \mathcal{Y}_h$임을 보이면 충분하다. 정의에 따라 $\mathcal{Y}_{h-1}$ ($\mathcal{Y}_{h}$)는 크기가 $h-1$ ($h$)인 포트폴리오 중에 함수 $v(\mathcal{Y}\cup\{k\})$를 최대화한다. 다시 말해 $\mathcal{Y}_{h-1}$과 $\mathcal{Y}_h$는 각각 단일 원소 포트폴리오 $\{k\}$와 최적으로 보완적인 학교 집합이다.
